A quantum parallel Markov chain Monte Carlo

### 2021-11-05 main.tex
breaktime

==============================

Quantum logic gates perform linear operations on qubits and take the form of unitary matrices $\U$ satisfying $\U^\dagger \U=\I$ for $\U^\dagger$ the conjugate transpose of $\U$. One terrifically important quantum gate is the \emph{Hadamard gate}
\begin{align}
\H = \frac{1}{\sqrt{2}} \begin{bmatrix}
1 & 1 \\
1 & -1 \end{bmatrix} \, .
\end{align}
We invite the Reader to check for themselves that $\H$ is indeed unitary and that its action maps $\ket{0}$ to $\ket{+}$ and $\ket{1}$ to $\ket{-}$.

>>>>

Quantum logic gates perform linear operations on qubits like $\ppsi$ and take the form of unitary matrices $\U$ satisfying $\U^\dagger \U=\I$ for $\U^\dagger$ the conjugate transpose of $\U$. One terrifically important quantum gate is the \emph{Hadamard gate}
\begin{align}
\H = \frac{1}{\sqrt{2}} \begin{bmatrix}
1 & 1 \\
1 & -1 \end{bmatrix} \, .
\end{align}
The Reader may verify that $\H$ is indeed unitary and that its action maps $\ket{0}$ to $\ket{+}$ and $\ket{1}$ to $\ket{-}$.
